---
title: "R-Ladies Global's disapproval of DataCamp"
author: "R-Ladies Global Leadership Team"
date: "2019-04-08"
description: "R-Ladies Global's disapproval of DataCamp's handling of sexual assault"
tags: 
- community
categories:
- r-ladies
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

_This blog post is a slightly extended version of the [official statement the R-Ladies Global organization made via Twitter](https://twitter.com/RLadiesGlobal/status/1114507499728769024), in a form that is easier to share. The views expressed here are the views of the R-Ladies Global Team signing at the end of this post and do not represent the R-Ladies community at large._

# Why we condemn DataCamp's handling of sexual assault

We are very disappointed by the way DataCamp handled the sexual assault of an employee by a C-level executive. We strongly support the target who is a member of our community and condemn DataCamp for their lack of accountability and transparency around this issue. As remarked by [`no_reply`](https://twitter.com/no_reply/status/1113923302915837958), DataCamp "quietly published [a "community" post](https://www.datacamp.com/community/blog/note-to-our-community), in which they admit an executive sexually assaulted ("uninvited physical contact") an employee."

We applaud the collective action from the DataCamp instructor community for pushing for this accountability and transparency, with countless hours of working with the assault target, DataCamp employees, executives, content developers, and members of the R Community at large. As [explained by Erin LeDell](https://twitter.com/ledell/status/1114238844503609344), "After *many months* of collective negotiating by the instructor community to demand more transparency & accountability, [DataCamp] still did nothing. Their public announcement is a response to a letter we sent to DataCamp one day prior, signed by over 100 DataCamp instructors.".

We are not satisfied with the response from DataCamp. As underlined by [Julia Silge](https://twitter.com/juliasilge/status/1113996214561923072) and [Mara Averick](https://twitter.com/dataandme/status/1113939480300355584), the post used "details in victim-blaming ways".

# How could you stand up for more accountability?

If you are unsatisfied with DataCamp's actions and response, you could use your voice and your wallet to vote for more accountability. Below we have summarized ideas about how you can show your disapproval of DataCamp’s response, as collected from a [thread started by Jesse Mostipak](https://twitter.com/kierisi/status/1113945904698892289), with contributions from [Chris Engelhardt](https://twitter.com/EngelhardtCR), [Laura Ación](https://twitter.com/_lacion_/status/1113960425174052864), [Bruna Wunderwald](https://twitter.com/bwundervald/status/1114907322441244672), and [Erin LeDell](https://twitter.com/ledell/status/1115138789293211649).

1. Cancel your subscription.

2. Cancel your organization's subscription.

3. Remove links/recommendations to use DataCamp from your material.

4. Stop developing content/lectures for them. Folks who are not customers can alter behavior as well.

5. Take your DataCamp stickers off your laptop/car/water bottle/ etc. 

6. Just say "No" when they ask you to do a podcast.

7. Don't accept DataCamp as a sponsor of events you organize.

8. Delete your account (even if you don't have a paid subscription anymore).

9. Remove your tweets containing “DataCamp" by searching `DataCamp from:@youruser` (replace `@youruser` by your own handle) in Twitter search and deleting the old tweets that endorsed them in any way.

10. Unfollow Datacamp from social media like Twitter, Facebook, etc.

11. If you are working on a course or project for DataCamp, you can put your work on hold until you feel that appropriate and sufficient action has been taken on behalf of DataCamp.


These are ideas of what you could do. It is up to you to decide what you want or can do, given your personal situation. 

We feel for anyone who finds themselves in a difficult situation regarding their involvement (whether as employees or content developers) with DataCamp. Please be assured that our criticism is directed at the leadership team of DataCamp who made these decisions and who have the opportunity and power to rectify this situation.

Any women or gender minorities who want to discuss this matter (or any other) with other R-Ladies, please join our [community slack](https://rladies-community-slack.herokuapp.com/).

Let's keep working on a safe community for everyone!

-- _The R-Ladies Global Leadership Team (Gabriela de Queiroz, Hannah Frick, Erin LeDell, and Claudia Vitolo) with Laura Ación and Maëlle Salmon (members of the [R-Ladies Global Team](https://rladies.org/about-us/team/))_

# [Update] Other posts and tweets from the community about DataCamp

+ 2019-04-05, Greg Wilson - [The Worst Behavior](http://third-bit.com/2019/04/05/the-worst-behavior.html)

+ 2019-04-12, Noam Ross - [Don’t Take My DataCamp Course, There Must be Consequences for Sexual Assault](https://noamross.github.io/datacamp-sexual-assault/)

```{r echo=FALSE}
blogdown::shortcode('tweet', '1116709899159916544')
```

+ 2019-04-12, Bob Rudis - [A Note to Our Community On How To Hide Your Content From Search Engines](https://rud.is/b/2019/04/12/a-note-to-our-community-on-how-to-hide-your-content-from-search-engines/)

+ 2019-04-14, Steph Locke - [DataCamp Sponsorship of satRday Events](https://satrdays.org/blog/2019/04/14/datacamp-sponsorship/)

+ 2019-04-15, Dhavide Aruliah - [A note to our community on building trust](https://dhavide.github.io/a-note-to-our-commuity-on-building-trust.html)

+ 2019-04-15, Greg Wilson - [An Exchange with DataCamp](http://third-bit.com/2019/04/15/an-exchange-with-datacamp.html)

+ 2019-04-16, Julia Silge - [Writing a letter to DataCamp ](https://juliasilge.com/blog/datacamp-misconduct/)

```{r echo=FALSE}
blogdown::shortcode('tweet', '1116743032492253185')
```
