---
title: "Mentoring program"
slug: mentoring
output: html_document
---

```{css 'css', echo=FALSE}
.grid {
  display: flex;
  flex-wrap: wrap; 
  justify-content: space-between;
  list-style-type: none;
  font-size: 1.5vh;
  padding: 0px;
  overflow: wrap;
}

.grid-item {
  flex-grow: 1 0 0; 
}

.left-banner{
  display: block;
  margin: 0;
  padding: 0;
}

.card {
  display: flex;
  height: 190px;
  width: 325px;
  align-item: center;
}

@media only screen and (max-width: 600px) {
  .card {
    width: 100%;
  }
}

@media only screen and (max-width: 1400px) {
  .card {
    width: 100%;
  }
}

.card a {
  background-color: #88398a;
  color: white;
  text-orientation: sideways-right;
  writing-mode: vertical-rl;
  height: 60%;
  font-weight: bold;
  font-size: 1.15vh;
  padding-top: .6em;
  margin:0;
}

.card p {
  background-color: #88398a;
  color: white;
  text-orientation: sideways-right;
  writing-mode: vertical-rl;
  height: 40%;
  font-weight: bold;
  font-size: 1.15vh;
  margin:0;
}

.crop {
  height: 100%;
  width: 175px;
  overflow: hidden;
}

.crop img {
  height: 100%;
  width: 175px;
  overflow: hidden;
  object-fit: cover;
}

.statement {
  flex-grow: 1 1 0;
  height: 100%;
  border: thick solid #88398a;
  padding: .2em;
}

.statement-inner {
  border: double #a7a9ac;
  padding: 1.5vh;
  height: 100%;
  width: 100%; 
}

.statement q {
  color: #727272; 
  font-weight: bold;
  font-size: 1.5vh;
  line-height: 0.1;
}

```
 
Never worry, there is always an R-Lady mentor to walk with you!

The main objective of the R-Ladies Mentoring Program is to help organisers conduct successful meetups and keep their chapters active.
 
Organizing an R-Ladies chapter involves a series of tasks that can feel overwhelming to a new organiser. 
However, a number of experienced R-Ladies organisers are willing to mentor new ones and provide some great advice.

For mentors, this is an opportunity to help build the community, learn about the realities of other chapters, gain experience as a mentor, and contributing to R-Ladies' goals.

Do you want to be a part of the mentoring program? 
Join us by filling out [this short form](https://tinyurl.com/rladies-mentoring)

## Experiences from the program

```{r, include = FALSE}
library(dplyr)
mentoring <- tibble::tribble(
  ~ mentor_name, ~mentor_chapter, ~mentee_name, ~mentee_chapter, ~img,  ~ statement,  ~twitter, ~ url,
  "Erin Ledell", "R-Ladies SF", "Athanasia M. Mowinckel", "R-Ladies Oslo", "https://drmowinckels.io/img/profile.png", "some really awesome statement", "RLadiesOslo", "www.google.com",
  "Erin Ledell", "R-Ladies SF", "Athanasia M. Mowinckel", "R-Ladies Oslo", "https://www.h2o.ai/wp-content/uploads/2018/08/erin_ledell.jpg", "some really awesome statement", "RLadiesOslo", "www.google.com",  "Erin Ledell", "R-Ladies SF", "Athanasia M. Mowinckel", "R-Ladies Oslo", "https://drmowinckels.io/img/profile.png", "some really awesome statement", "RLadiesOslo", "www.google.com")

mentoring <- mentoring %>%
  mutate(
    div = paste0(
      "<div class='card'>",
      "<div class='left-banner'>",
      "<a href='https://twitter.com/", twitter, "' style='float: top;'>@", twitter,"</a>",
      "<p style='float: bottom;'>Mentoring program</a>",
      "</div>",
      # "<a href='", url, "'>",
      "<span style='display: flex; align-items:center; '>",
        "<div class='crop'><img src='", img, "'></div>",
        "<div class='statement'><div class='statement-inner'>",
        '<q>" ', statement, ' "</q>',
      "</div></div>",
      "</div>",
      "<div><p>",
         "<b>Mentor: </b>", mentor_name, " (", mentor_chapter, ")<br>",
         "<b>Mentee: </b>", mentee_name, " (", mentee_chapter, ")",
      "</p><div>",
      # "</a>",
      "</div>"
    ) 
  )
```

<ul class="grid">
```{r, results='asis', echo = FALSE}
for(i in 1:nrow(mentoring)){
  cat("<li class='grid-item'>")
  cat(mentoring$div[i])
  cat("</li>")
}
```
</ul>


