---
title: "Mentoring program"
slug: mentoring
output: html_document
---

```{css 'css', echo=FALSE}
.grid {
  display: flex;
  flex-wrap: wrap; 
  justify-content: space-between;
  list-style-type: none;
  font-size: 1.5vh;
  padding: 0px;
  overflow: wrap;
}

.grid-item {
  flex-grow: 1 0 0; 
}

@media only screen and (max-width: 600px) {
  .card {
    width: 100%;
  }
}

.grid-item img {
  height: 230px;
  width: 500px;
  overflow: hidden;
  object-fit: cover;
}

button{
  background-color: #88398a;
  border-radius: 1em;
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
}

button:hover {
  background-color: #88398aee;
}
```
 
Never worry, there is always an R-Lady mentor to walk with you!

The main objective of the R-Ladies Mentoring Program is to help organisers conduct successful meetups and keep their chapters active.
 
Organizing an R-Ladies chapter involves a series of tasks that can feel overwhelming to a new organiser. 
However, a number of experienced R-Ladies organisers are willing to mentor new ones and provide some great advice.

For mentors, this is an opportunity to help build the community, learn about the realities of other chapters, gain experience as a mentor, and contributing to R-Ladies' goals.

<center>
<a href='https://tinyurl.com/rladies-mentoring' target="_blank"><button>Join the program</button></a>
</center>

## Experiences from the program

```{r, include = FALSE}
library(dplyr)
mentoring <- tibble::tribble(
  ~ mentor_name, ~mentor_chapter, ~mentee_name, ~mentee_chapter, ~img,  ~url,
  "Erin Ledell", "R-Ladies SF", "Nadeja Sero", "R-Ladies Cotonou", "/images/mentoring/cotonou.png", "www.google.com")

mentoring <- mentoring %>%
  mutate(
    div = paste0(
      "<a href='", url, "'>",
        "<img src='", img, "'>",
      "</a>",
      "<div><p>",
         "<b>Mentor: </b>", mentor_name, " (", mentor_chapter, ")<br>",
         "<b>Mentee: </b>", mentee_name, " (", mentee_chapter, ")",
      "</p><div>"
    ) 
  )
```

<ul class="grid">
```{r, results='asis', echo = FALSE}
for(i in 1:nrow(mentoring)){
  cat("<li class='grid-item'>")
  cat(mentoring$div[i])
  cat("</li>")
}
```
</ul>


