---
title: "R-Ladies Directory"
output:
  html_document:
    keep_md: yes
slug: directory
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, include = FALSE, echo = F)

library(leaflet)
library(widgetframe)
library(ggmap)
library(purrr)
library(dplyr)

#register_google(key = "AIzaSyCZ2J7fgbcyROdMYwr9fTzKQ2dCgZKqsMU")

files <- jsonlite::read_json("../d/directory.json")

geocodes <- map_dfr(files, magrittr::extract, c("city", "country")) %>% 
  distinct() %>% 
  mutate(string = paste0(city, ", ", country),
         url = paste0("http://127.0.0.1:4321/", 
                      stringr::str_replace_all(country, " ", "")),
         popup = paste0("<a target='_blank' href='", url, "'>", string, "</a>")) %>% 
  cbind(map_dfr(.$string, geocode))

m <- leaflet(geocodes) %>%
  setView(lng = 0, lat = 0, zoom = 01) %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addMarkers(lng = ~lon, lat = ~lat, popup = ~popup)
```

```{r map, include=T}
frameWidget(m)
```

**We would love more R-Ladies to appear in our Directory! Please fill out** [our form]()! It only takes a few minutes, and soon your profile will be online.

If you want to **update** your profile just fill the same form and drop us a line in the comment box saying you want to update your profile!

Or you can just email us at speakers[at]rladies[dot]org with any relevant info about yourself – easy!

```{r}
for (country in geocodes$country) {
  slug <- stringr::str_replace_all(country, " ", "")
  filename <- paste0(slug, '.Rmd')
  file.create(filename)
  
  sink(filename)
  cat(paste0('---
title: "', country,' speakers"
output: html_notebook
data: "', country, '"
type: "directory"
---

\`\`\`{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, include = FALSE, echo = F)
\`\`\`'))
  sink()
}

```